\begin{thebibliography}{99}
	\bibitem{Vision0}
	Matts-Ake Belina, Per Tillgrena, and Evert Vedungd, Vision Zero – a road safety policy innovation,
	\textit{International Journal of Injury Control and Safety Promotion}, \textbf{19}, No. 2, 171-179, 2012. 
	\bibitem{dtp_data}
	\href{https://dtp-stat.ru}
	{Проект <<Карта ДТП>>}
	\bibitem{DBSCAN}
	Ester, M., H. P. Kriegel, J. Sander, and X. Xu, A Density-Based Algorithm for Discovering Clusters in Large Spatial Databases with Noise,
	\textit{Proceedings of the 2nd International Conference on Knowledge Discovery and Data Mining}, 226-231, 1996.
	\bibitem{prophet}
	\href{https://peerj.com/preprints/3190.pdf}{Sean J. Taylor, Benjamin Letham, Forecasting at scale, \textit{The American Statistician}, (2018).}
	\bibitem{CKS}
	J. Cohen, A coefficient of agreement for nominal scales, \textit{Educational and Psychological measurement}, \textbf{20}, No. 1, (1960).
	\bibitem{MCC_intro}
	Matthews B. W., Comparison of the predicted and observed secondary structure of T4 phage lysozyme,
	\textit{Biochimica et Biophysica Acta (BBA) - Protein Structure}, \textbf{405}, 442–451, (1975).
	\bibitem{MCC_2000}
	P. Baldi, S. Brunak, Y. Chauvin, C. A. Andersen, H. Nielsen, Assessing the accuracy of prediction algorithms for classification:
	an overview, \textit{Bioinformatics}, \textbf{16}, No. 5, 412-424, 2000.
	\bibitem{MCC_new}
	D. Chicco, M. J. Warrens and G. Jurman, 
	The Matthews Correlation Coefficient (MCC) is More Informative Than Cohen’s Kappa and Brier Score in Binary Classification Assessment,
	\textit{IEEE Access}, \textbf{9}, 78368-78381, 2021.
	\bibitem{IsolForest}
	\href{https://cs.nju.edu.cn/zhouzh/zhouzh.files/publication/icdm08b.pdf}
	{Fei Tony Liu, Kai Ming Ting, Zhi-Hua Zhou, Isolation Forest, \textit{Data Mining}, 2008.}
	\bibitem{1SVM}
	\href{https://papers.nips.cc/paper/1999/file/8725fb777f25776ffa9076e44fcfd776-Paper.pdf}
	{Bernhard Scholkopf, Robert Williamson, Alex Smola, John Shawe-Taylort, John Platt, Support Vector Method for Novelty Detection,
	\textit{NIPS}, 1999.}
	\bibitem{LOF}
	Breunig, M. M., Kriegel, H. P., Ng, R. T., Sander, J, LOF: identifying density-based local outliers, \textit{ACM sigmod record}, 2000.
\end{thebibliography}
